---
title: "Exploratory Analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = "CairoPNG", warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r load-packages}
pacman::p_load(
  "tidyverse"
)

# remotes::install_github('context-dependent/bptheme')
```


## Introduction

### Purpose

Use this notebook to present your exploratory analysis of the house prices data. 

### Load data


```{r load-data}
dat <- read_csv("data/raw/housedata.csv")
```

### Univariate distributions

illustrate the univariate distributions here. Use histograms or density plots for continuous variables, and bar charts for categorical variables. 

### Multivariate distributions

illustrate multivariate distributions here. Focus on illustrating the relationships between price and the other variables. Use scatter plots, box plots, and facets where appropriate. 

### Data cleaning choices

- are any transformations appropriate? 
- which variables appear to ave the strongest relationship with price? 


